Flexibility of interactions depends on habitat suitability

### 2019-08-30 paper/manuscript.Rmd
Model comparison table now based only on WAIC

fig_conditional_effects_legend <- 
  paste0("Conditional effects of predictors in our baseline model. The predicted values of the number of interacting species are based on a hypothetical community with ",
         median_n_pla, " plants and ", 
         median_n_ani, " pollinators",
         ". These values correspond to the median number of species in each guild respectively. In each panel we condition on the mean values of all other predictors in the model, mean values for each predictor are indicated with a vertical dashed line. For model fitting, we scaled all predictors to have mean of zero and unit variance. However, with the exception of environmental niche size, here we show the unscaled predictors to facilitate interpretation. To illustrate the uncertainity around the fitted estimates we plot the fits of 100 independent draws from the posterior distribution. The thick lines indicate the mean values of the response distribution. As there was no interaction between guild and generality or the number of possible interactions, for these two predictors we only show conditional the conditional effect of pollinators.")
readd(fig_conditional_effects)
```

```{r tab-model-comparison-table}
loadd(model_ranking)

waic_scores <- as.data.frame(model_ranking$waic) %>%
  tibble::rownames_to_column(var = "formula") %>%
  dplyr::select(formula, waic)

loo_scores <- as.data.frame(model_ranking$loo) %>%
  tibble::rownames_to_column(var = "formula") %>%
  dplyr::select(formula, elpd_diff, se_diff,  looic)

loo_scores %>%
  dplyr::inner_join(waic_scores, by = "formula") %>%
  dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
                formula = kableExtra::cell_spec(formula, format = "latex", 
                                                bold =nchar(formula) == max(nchar(formula)))) %>%
  knitr::kable("latex", 
               booktabs = TRUE, 
               digits = c(0,0,1,0,0), 
               format.args = list(big.mark = ","), 
               col.names = c("predictors", "$\\Delta$", "$SE_{\\Delta}$", "IC", "WAIC"),
               escape = FALSE,
               linesep = "",
               caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives. We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO). The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking. We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
  kableExtra::kable_styling(font_size = 8) %>%
  kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
```

>>>>

fig_conditional_effects_legend <- 
  paste0("Conditional effects of predictors in our baseline model. The predicted values of the number of interacting species are based on a hypothetical community with ",
         median_n_pla, " plants and ", 
         median_n_ani, " pollinators",
         ". These values correspond to the median number of species in each guild respectively. In each panel we condition on the mean values of all other predictors in the model, mean values for each predictor are indicated with a vertical dashed line. For model fitting, we scaled all predictors to have mean of zero and unit variance. However, with the exception of environmental niche size, here we show the unscaled predictors to facilitate interpretation. To illustrate the uncertainity around the fitted estimates we plot the fits of 100 independent draws from the posterior distribution. The thick lines indicate the mean values of the response distribution. As there was no interaction between guild and generality or the number of possible interactions, for these two predictors we only show conditional the conditional effect of pollinators.")

readd(fig_conditional_effects)
```

```{r tab-model-comparison-table}
model_ranking$waic %>%
  purrr::map(~.$estimates["waic", ]) %>%
  purrr::map_df(~tibble::tibble(estimate = .[1], se = .[2]), .id = "formula") %>%
  dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
                formula = kableExtra::cell_spec(formula, format = "latex", 
                                                bold =nchar(formula) == max(nchar(formula)))) %>% 
   knitr::kable("latex", 
               booktabs = TRUE, 
               digits = c(0,0,0), 
               format.args = list(big.mark = ","), 
               col.names = c("predictors", "WAIC", "SE"),
               escape = FALSE,
               linesep = "",
               caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives. We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO). The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking. We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
  kableExtra::kable_styling(font_size = 8) #%>%
  # kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
# 
# waic_scores <- as.data.frame(model_ranking$waic) %>%
#   tibble::rownames_to_column(var = "formula") %>%
#   dplyr::select(formula, waic)
# 
# loo_scores <- as.data.frame(model_ranking$loo) %>%
#   tibble::rownames_to_column(var = "formula") %>%
#   dplyr::select(formula, elpd_diff, se_diff,  looic) 
# 
# loo_scores %>%
#   dplyr::inner_join(waic_scores, by = "formula") %>%
#   dplyr::mutate(formula = translate_model_formula(formula, "long-abv"), 
#                 formula = kableExtra::cell_spec(formula, format = "latex", 
#                                                 bold =nchar(formula) == max(nchar(formula)))) %>%
#   knitr::kable("latex", 
#                booktabs = TRUE, 
#                digits = c(0,0,1,0,0), 
#                format.args = list(big.mark = ","), 
#                col.names = c("predictors", "$\\Delta$", "$SE_{\\Delta}$", "IC", "WAIC"),
#                escape = FALSE,
#                linesep = "",
#                caption = "Comparison in out of sample predictive power of the baseline model (bold) and their alternatives. We rank models by their expected log predictive density based on their leave-one-out cross-validation information criterion (LOO). The standard error of the LOO difference provides rough guidance to the uncertainty of the model ranking. We also show the Wanatabe-Akaike information criterion (WAIC) of each model for comparison.") %>%
#   kableExtra::kable_styling(font_size = 8) %>%
#   kableExtra::add_header_above(c(" " = 1, "LOO" = 3, " " = 1))
```
